\documentclass[12pt]{article}
\usepackage{cls}

\begin{document}

\begin{center}
{\fontfamily{phv}\selectfont \bfseries Acknowledgments}
\end{center}

\vspace{1em}

The 48th CLS conference (April 19-21, 2012) represented the culmination of a yearlong process for us. We were proud to say upon its completion that we succeeded in doing so, and we are proud to now present its proceedings here. 

Following a long standing tradition, CLS brought together a diverse array of topics of research as well as points of view within each field. This led to a lively discussion among scholars of different backgrounds and methodologies. Our main sessions featured talks on syntax, semantics, phonology, phonetics, historical linguistics, sociolinguistics, and more, featuring invited presentations from Marcel den Dikken, Kai von Fintel, and Alan Yu. In addition, we had three parasessions, meant to draw attention to areas of linguistics that are seeing a promising combination of innovative methods or theoretical questions, and meant to bring together scholars with overlapping interests.  The parasessions were the following: ``Meaning and cognition'', with invited speaker Nausicaa Pouscoulous, ``Agreement", featuring Sandra Chung's invited presentation, and ``Historical Phonology and Morphology", hosting invited speaker Adam Albright.  

Due to editorial arrangement, John Goldsmith`s invited paper "Theory, Kernels, Data, Methods" from CLS 46 (April 8-10, 2010) is published in the present volume.

There are so many people to thank, and this page will surely not be enough to give credit where it is due. However, we would like to first thank the undergraduate and graduate students at the University of Chicago without whose volunteered support the conference could not have existed; particular thanks go to prior CLS officers, especially Chieu Nguyen, whose astonishing computational skills came very handy in the frenzy of deciding accepted abstracts and putting together the conference booklet. We would like to thank the faculty at the University of Chicago, whose advice was much needed and welcome. Special thanks go to Chris Kennedy, whose guidance proved crucial to handle unexpected challenges, and Jason Merchant, for delivering a heartfelt and grateful speech at the closing banquet. We would like to thank Vanessa Wright for invaluable administrative support throughout the planning and execution of the conference. Last but not least, we would like to thank CLS 50 officers, and Adam Singerman in particular, for their editorial assistance.

We would like to thank the University of Chicago for its many vital provisions, and we are very grateful for the crucial financial and logistical support we received from the Office of the Reynolds Club and Student Activities; the Franke Institute for the Humanities; and the Humanities Division Graduate Student Council. 

Lastly, we would like to thank the attendees of CLS 48, those who presented as well as those who did not, who made the conference stimulating and memorable.

\vspace{1em}

\noindent \textit{CLS 48}\\
Andrea Beltrama\\
Tasos Chatzikonstantinou\\
Jackson L. Lee\\
Mike Pham\\
Diane Rak


\end{document}
